02_DESeq_characterization

### 2019-11-23 analysis/03_DESeq2_characterization.Rmd
images:

  volcano <- data %>%
    ggplot(aes(x = lfc, y = logpadj)) + 
    geom_point(aes(color = direction, shape = tissue), size = 1, alpha = 0.75, na.rm = T) + 
    theme_minimal() +
    scale_color_manual(values = mycolors,
                       name = " ",
                       drop = FALSE) +
    ylim(c(0,30)) +  
    xlim(c(-8,8)) +
    labs(y = "-log10(p)", x = " ")  +
    theme(legend.position = "none",
          legend.direction = "horizontal",
          legend.spacing.x = unit(-0.1, 'cm'),
          legend.margin=margin(t=-0.25, r=0, b=0, l=0, unit="cm"),
          panel.grid = element_blank()) +
    scale_shape_manual(values = myshapes)
  return(volcano)
}

@@

pituitary <- plot_grid(a + 
                       theme(axis.title.x = element_blank(), axis.text.x = element_blank()) +
                       labs(y = "pituitary \n -log10(p)"),
          b + theme(axis.title = element_blank(), axis.text = element_blank()),
          c + theme(axis.title = element_blank(), axis.text = element_blank()),
          d + theme(axis.title = element_blank(), axis.text = element_blank()), 
          e + theme(axis.title = element_blank(), axis.text = element_blank()),
          f + theme(axis.title = element_blank(), axis.text = element_blank()),
          g + theme(axis.title = element_blank(), axis.text = element_blank()),
          h + theme(axis.title = element_blank(), axis.text = element_blank()), 
          nrow = 1,  rel_widths = c(1.75,1,1,1,1,1,1,1,1))
pituitary

>>>>

  volcano <- data %>%
    ggplot(aes(x = lfc, y = logpadj)) + 
    geom_point(aes(color = direction, shape = tissue), size = 2, 
               alpha = 0.75, na.rm = T) + 
    theme_minimal() +
    scale_color_manual(values = mycolors,
                       name = " ",
                       drop = FALSE) +
    ylim(c(0,30)) +  
    xlim(c(-8,8)) +
    labs(y = "-log10(p)", x = " ")  +
    theme(legend.position = "none",
          legend.direction = "horizontal",
          legend.spacing.x = unit(-0.1, 'cm'),
          legend.margin=margin(t=-0.25, r=0, b=0, l=0, unit="cm"),
          panel.grid = element_blank()) +
    scale_shape_manual(values = myshapes)
  return(volcano)
}

@@

pituitary <- plot_grid(a + 
                       theme(axis.title.x = element_blank(), axis.text.x = element_blank()) +
                       labs(y = "pituitary \n -log10(p)"),
          b + theme(axis.title = element_blank(), axis.text = element_blank()),
          c + theme(axis.title = element_blank(), axis.text = element_blank()),
          d + theme(axis.title = element_blank(), axis.text = element_blank()), 
          e + theme(axis.title = element_blank(), axis.text = element_blank()),
          f + theme(axis.title = element_blank(), axis.text = element_blank()),
          g + theme(axis.title = element_blank(), axis.text = element_blank()),
          h + theme(axis.title = element_blank(), axis.text = element_blank()), 
          nrow = 1,  rel_widths = c(1.75,1,1,1,1,1,1,1,1))
pituitary
```
